Early Observations of the Type Ia Supernova \abc:\\ A Case of Interaction with Nearby, Unbound Material and/or Strong Ejecta Mixing

### 2018-05-22 doc/ms.tex
update observations section

% This paper is organized as follows: Section \ref{sec:obs} describes
% photometric and spectroscopic observations of \abc. Section
% \ref{sec:usual_staff} establishes that \abc\ is a normal SN Ia
% in NGC\,5221. Section \ref{sec:first_light} analyzes the early
% light curve and spectra.

@@

During the spring of 2016, the iPTF survey observed the field of \abc\ every
night during dark time in either the $g_\mathrm{PTF}$ or $R_\mathrm{PTF}$
band.\footnote{P48 observations of \abc\ are reported in the $g_\mathrm{PTF}$
and $R_\mathrm{PTF}$ filters throughout, which are similar to the SDSS $g'$
and Mould-$R$ filters, respectively (see \citealt{2012PASP..124..854O} for
details on PTF calibration). The correction from the $g_\mathrm{PTF}$ and
$R_\mathrm{PTF}$ filters to SDSS $g'$ and $r'$ requires knowledge of the
intrinsic source color (see Eqns.~1 and 2 in \citealt{2012PASP..124..854O}).
The spectral diversity of SNe Ia in the days after explosion is poorly
constrained, and as a result the color terms for \abc\ at these epochs are
unknown. We proceed by assuming the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$
calibration is on the AB system, which strictly speaking is incorrect, but
this does not fundamentally alter any of our conclusions.} Survey observations
were conducted with the CFH12K camera \citep{2008SPIE.7014E..4YR} on the
Palomar Observatory 48-inch telescope (P48; \citealt{2009PASP..121.1395L}).
Images were processed by the IPAC image-subtraction pipeline, which subtracts
background galaxy light using deep pre-SN images, and performs forced
point-spread-function (PSF) photometry at the location of the SN
\citep{2017PASP..129a4002M}. The photometry is then calibrated to the PTF
photometric catalog \citep{2012PASP..124..854O}.

\begin{figure}[htb] 
    \centering
    \includegraphics[width=3.35in]{logLC_with_colors.pdf} 
    \caption{
    %
    The $g$-band light curve of \abc, with 5-$\sigma$ upper limits shown as
    downward arrows. Observations from different telescopes are shown with
    different symbols. The lower axis shows time measured in
    rest-frame days relative to $t_0$ (see \S\ref{sec:lc_fit}), while
    the upper axis shows time relative to $B$-band maximum. Note that the
    horizontal axis is shown with a linear scale for $-2 \; \mathrm{d} \le t -
    t_0 \le 3 \; \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \;
    \mathrm{d}$. Vertical black ticks show epochs of spectroscopic
    observations. }
% 
    \label{fig:lightcurve} 
\end{figure}

After discovery, $g'$, $r'$ and $i'$-band photometry was obtained
with the SED Machine (SEDm; \citealt{2017arXiv171002917B}) mounted on the
Palomar Observatory 60-inch telescope (P60). We utilized the Fremling
Automated Pipeline (\texttt{FPipe}; \citealt{2016A&A...593A..68F}) to subtract
galaxy light from the SEDm images using archival Sloan Digital Sky Survey
(SDSS) images as a reference. This pipeline then performed forced-PSF
photometry at the location of \abc, which is calibrated to the SDSS catalog
\citep{2014ApJS..211...17A}.

The Las Cumbres Observatory (LCO) 1-m telescope network obtained
$BVg'r'i'$ photometry. PSF photometry was measured on these images using the
\texttt{lcogtsnpipe} pipeline \citep{2016MNRAS.459.3939V}. The \textit{BV}
magnitudes are calibrated to the Fourth USNO CCD Astrograph Catalog
\citep{2013AJ....145...44Z}, and the \textit{g'r'i'} magnitudes are calibrated
to SDSS Data Release 6 \citep{2008ApJS..175..297A}.

The Reionization and Transients InfraRed (RATIR) camera on the autonomous
1.5\,m Harold L. Johnson Telescope
\citep{2012SPIE.8446E..10B,2012SPIE.8444E..5LW} was used to observe \abc\ in
the $r'i'ZYJH$ filters. By design, RATIR lacks a cold shutter, which means IR
dark frames are not available. Laboratory testing, however, confirms that the
dark current is negligible in both IR detectors \citep{2012SPIE.8453E..1OF}.

The RATIR data were reduced, coadded, and analyzed using standard CCD and IR
processing techniques in \texttt{IDL}, \texttt{Python}, \texttt{SExtractor}
\citep{1996A&AS..117..393B}, and \texttt{SWarp}. Aperture photometry is
obtained following the methods described in \citet{2014AJ....148....2L}. The
$r'i'Z$ filters are calibrated to SDSS \citep{2014ApJS..211...17A}, while the
$JH$ filters are calibrated to the Two Micron All Sky Survey
\citep{2006AJ....131.1163S}. For the $Y$-band calibration, we used an
empirical relation in terms of the $J$ and $H$ magnitudes derived from the
United Kingdom Infrared Telescope (UKIRT; \citealt{2007A&A...467..777C}) Wide
Field Camera observations \citep{2009MNRAS.394..675H}.

The \textit{Swift} satellite observed \abc\ on 14 epochs, beginning
$\sim$15\,d pre-maximum light through $\sim$22\,d post maximum. The SN flux is
measured via aperture photometry on Ultraviolet-Optical Telescope (UVOT)
images via the usual procedures in \texttt{HEASoft}, including corrections for
coincidence loss and aperture loss. The image counts are converted to physical
fluxes using the latest calibration \citep{2011AIPC.1358..373B}. There are no
pre-SN UVOT images at the SN location in the \textit{Swift} archive. Visual
inspection of the UVOT images suggests negligible host-galaxy contamination in
our UVOT flux measurements. No X-ray emission is detected from \abc\ by the
\textit{Swift} X-ray Telescope (XRT).

The $g$-band discovery and follow-up data of \abc\ are illustrated in
Figure~\ref{fig:lightcurve}. The photometry is shown in the AB system. As
previously noted the color terms necessary to convert $g_\mathrm{PTF}$ to the
AB system are unknown and assumed to be zero.

Spectroscopic observations of \abc\ were taken with a variety of telescopes
and instruments over multiple epochs beginning $\sim$2\,d after
discovery and ending $\sim$2 months after $B$-band maximum. An
observing log is listed in Table \ref{tab:spec_obs_log}. The spectra were
reduced using standard procedures in
\texttt{IDL}/\texttt{Python}/\texttt{Matlab}. The optical spectral evolution
of \abc\ is illustrated in Figure \ref{fig:spec_seq}, which excludes
high-resolution Very Large Telescope (VLT) spectra for clarity.

\begin{deluxetable}{cccccc}
  \tablecaption{Spectroscopic observations of \abc\ \label{tab:spec_obs_log}}
  \tabletypesize{\footnotesize}
  \tablehead{
    \colhead{Observation} & \colhead{SN} & \colhead{} &
    \colhead{} & \colhead{Range} \\
    \colhead{MJD} & \colhead{phase} & \colhead{Telescope} &
    \colhead{Instrument} & \colhead{(\AA)}
  }
  \startdata
  $57483.26$ & $-15.9$ & DCT & DeVeny\tablenotemark{1} & $3301$--$7499$ \\
  $57483.88$ & $-15.3$ & Gemini-North & GMOS\tablenotemark{2} & $3800$--$9200$ \\
  $57484.51$ & $-14.7$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
  $57486.51$ & $-12.7$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
  $57488.38$ & $-10.9$ & Keck-I & LRIS\tablenotemark{4} & $3055$--$10411$ \\
  $57489.51$ & $ -9.8$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
  $57490.40$ & $ -8.9$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
  $57491.55$ & $ -7.8$ & LCO-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
  $57492.20$ & $ -7.2$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24550$ \\
  $57494.00$ & $ -5.4$ & VLT & UVES\tablenotemark{7} & \\
  $57503.32$ & $ +3.7$ & LCO-2m & FLOYDS\tablenotemark{5} & $3300$--$9999$ \\
  $57506.00$ & $ +6.3$ & NOT & ALFOSC\tablenotemark{8} & $3602$--$8098$ \\
  $57508.27$ & $ +8.5$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
  $57518.42$ & $+18.5$ & Keck-I & LRIS\tablenotemark{4} & $3071$--$10208$ \\
  $57520.03$ & $+20.0$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24789$ \\
  $57529.40$ & $+29.2$ & LCO-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
  $57542.41$ & $+41.9$ & LCO-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
  $57550.40$ & $+49.7$ & LCO-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
  $57562.38$ & $+61.4$ & LCO-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
  \enddata
  \tablenotetext{1}{The Deveny Spectrograph \citep{2014SPIE.9147E..2NB}}
  \tablenotetext{2}{The Gemini Multi-Object Spectrograph \citep{2004PASP..116..425H}}
  \tablenotetext{3}{DEep Imaging Multi-Object Spectrograph \citep{2003SPIE.4841.1657F}}
  \tablenotetext{4}{Low-Resolution Imaging Spectrometer \citep{1995PASP..107..375O}}
  \tablenotetext{5}{FLOYDS \url{https://lco.global/observatory/instruments/floyds}}
  \tablenotetext{6}{X-shooter \citep{XShooter}}
  \tablenotetext{7}{Ultraviolet and Visual Echelle Spectrograph \citep{2000SPIE.4008..534D}}
  \tablenotetext{8}{The Andalucia Faint Object Spectrograph and Camera \url{http://www.not.iac.es/instruments/alfosc}}
\end{deluxetable}

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=5.5in]{spectra.pdf}
  \caption{
  Observed spectral sequence of \abc. The spectra are normalized by their
  median flux between 6000 and 7000$\,\textrm{\AA}$. The phase of each
  spectrum relative to the time of $B$-band maximum is shown.
  Telluric absorption bands are grayed out. Line identifications are provided
  for the spectral features discussed in the text. For clarity,
  high-resolution spectra obtained with the VLT have been omitted (see
  \citealt{2017A&A...606A.111F} for a detailed discussion of these spectra).}
  \label{fig:spec_seq}
\end{figure*}

@@

Separately, \citet{2015MNRAS.447.1531C} observe the 21-cm line in NGC\,5221
and measure a redshift of $0.0234$, which we adopt for the remaining analysis
in this paper.

@@

A detailed study of the reddening towards \abc\ is presented in a companion
paper \citep{2017A&A...606A.111F}. Briefly, the foreground Galactic extinction
toward \abc\ is $E(B-V) = 0.0279$\,mag \citep{2011ApJ...737..103S}.
High-resolution spectra of \abc\ show multiple absorption components for both
the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D doublets. Despite large
equivalent widths (EWs) for these lines, implying significant extinction
(e.g., \citealt{2012MNRAS.426.1465P), \citeauthor{2017A&A...606A.111F}~find
evidence for only a small amount of extintion.} The empirical relation between
the EW of \ion{Na}{1}\,D and extinction has a large scatter, and
\citet{2013ApJ...779...38P} have shown that \ion{Na}{1}\,D absorption is a
poor tracer of reddening in Type Ia SNe. Thus, we adopt $E(B-V) = 0.05 \,
\mathrm{mag}$ as the local extinction for \abc\ \citep{2017A&A...606A.111F}.
For the remainder of our analysis we assume a total, Galactic $+$ host galaxy,
line-of-sight extinction of $E(B-V) = 0.08 \, \mathrm{mag}$.

@@

Using the SuperNova IDentification (\texttt{SNID};
\citealt{2007ApJ...666.1024B}) package, we find the low-resolution spectrum of
\abc\ at $+18.8$\,d is best matched by normal SNe Ia. Several characteristic
features of a SN Ia, such as \ion{Si}{2} and \ion{S}{2}, can be easily
identified in \abc\ (Figure \ref{fig:spec_seq}). From the $+3.7 \, \mathrm{d}$
LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of $-12 \pm
2$\,\AA\ and $-55 \pm 5$\,\AA\ for the absorption features near 5750 and 6100
\AA, attributed to \ion{Si}{2}\,$\lambda\lambda$5972, 6355, respectively.
According to the \citet{2006PASP..118..560B} classification scheme, \abc\ is a
shallow silicon SN, similar to 1999aa-like SNe \citep{2009PASP..121..238B}.
In Figure~\ref{fig:branch_vel, the velocity evolution of the \abc\
\ion{Si}{2}$\,\lambda6355$ absorption minimum is compared to the median
evolution of the four spectroscopic subclasses from
\citet{2006PASP..118..560B}. The median evolution is defined using the sample
of SNe Ia in \citet{2012AJ....143..126B}. For each SN, we interpolate the
\ion{Si}{2} velocity, $v_{\mathrm{Si\,II}\,\lambda6355}$, to a fixed grid at
1\,d intervals. The curves are defined by the median
$v_{\mathrm{Si\,II}\,\lambda6355}$ at each point on the grid with at least 3
SNe (this prevents just 1 or 2 SNe from defining the evolution of the entire
subclass). The velocity evolution of \abc\ is most reminicent of the
shallow-silicon subclass.}

@@

We measure the (pseudo)bolometric luminosity, $L_{UVOIR}$, of \abc\ at peak
via trapezoidal integration of the reddening-corrected flux from the UV,
optical, and NIR (UVOIR) filters. The light curves in the individual filters
are interpolated so that $L_{UVOIR}$ is evaluated at common epochs in each
filter. From this integration, we measure a maximum luminosity $L_\mathrm{max}
= 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \; s}^{-1}$ for \abc. This value
is consistent with the normal SNe Ia studied in \citet{2016A&A...588A..84D}.
Following Arnett's rule \citep{1982ApJ...253..785A,
1985Natur.314..337A}, the mass of $^{56}$Ni synthesized in the explosion can
be derived from $L_\mathrm{max}$. Assuming a rise time of $19 \pm 3$\,d (see
\citealt{2006A&A...450..241S}) we find $M_\mathrm{Ni} = 0.6 \pm 0.1
M_\odot$.\footnote{A 17.9\,d rise time (\S\ref{sec:lc_fit}),
yields a consistent estimate of $M_\mathrm{Ni}$.}}

@@

Here we consider our suite of early observations of \abc, and compare our
findings with SN\,2011fe, a well-studied, nearby SN that was discovered
shortly after explosion
\citep{2011Natur.480..344N,2012ApJ...744L..17B,2014ApJ...784...85P}.

>>>>

@@

During the spring of 2016, the iPTF survey observed the field of \abc\ every
night during dark time in either the $g_\mathrm{PTF}$ or $R_\mathrm{PTF}$
band.\footnote{P48 observations of \abc\ are reported in the
$g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters throughout, which are similar
to the SDSS $g'$ and Mould-$R$ filters, respectively (see
\citealt{2012PASP..124..854O} for details on PTF calibration). The
correction from the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ filters to SDSS
$g'$ and $r'$ requires knowledge of the intrinsic source color (see
Equations (1) and (2) in \citealt{2012PASP..124..854O}). The spectral
diversity of SNe Ia in the days after explosion is poorly constrained, and
as a result the color terms for \abc\ at these epochs are unknown. We
proceed by assuming that the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$
calibration is on the AB system, which strictly speaking is incorrect, but
this does not fundamentally alter any of our conclusions.} Survey
observations were conducted with the CFH12K camera
\citep{2008SPIE.7014E..4YR} on the Palomar Observatory 48-inch telescope
(P48; \citealt{2009PASP..121.1395L}). Images were processed by the IPAC
image-subtraction pipeline, which subtracts background galaxy light using
deep pre-SN images and performs forced point-spread function (PSF)
photometry at the location of the SN \citep{2017PASP..129a4002M}. The
photometry is then calibrated to the PTF photometric catalog
\citep{2012PASP..124..854O}.

\begin{figure}[htb] 
    \centering
    \includegraphics[width=3.35in]{logLC_with_colors.pdf} 
    \caption{
    %
    The $g$-band light curve of \abc, with $5\sigma$ upper limits shown as
    downward-pointing arrows. Observations from different telescopes are
    shown with different symbols. The lower axis shows time measured in
    rest-frame days relative to $t_0$ (see \S\ref{sec:lc_fit}), while the
    upper axis shows time relative to $B$-band maximum. Note that the
    horizontal axis is shown with a linear scale for $-2 \; \mathrm{d} \le t
    - t_0 \le 3 \; \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \;
    \mathrm{d}$. Vertical black ticks show epochs of spectroscopic
    observations. }
% 
    \label{fig:lightcurve} 
\end{figure}

After discovery, $g'$-, $r'$-, and $i'$-band photometry was obtained with
the SED Machine (SEDm; \citealt{2017arXiv171002917B}) mounted on the Palomar
Observatory 60-inch telescope (P60). We utilized the Fremling Automated
Pipeline (\texttt{FPipe}; \citealt{2016A&A...593A..68F}) to subtract galaxy
light from the SEDm images using archival Sloan Digital Sky Survey (SDSS)
images as a reference. This pipeline then performed forced-PSF photometry at
the location of \abc, which is calibrated to the SDSS catalog
\citep{2014ApJS..211...17A}.

The Las Cumbres Observatory (LCO) 1\,m telescope network obtained $BVg'r'i'$
photometry. PSF photometry was measured on these images using the
\texttt{lcogtsnpipe} pipeline \citep{2016MNRAS.459.3939V}. The \textit{BV}
magnitudes are calibrated to the Fourth USNO CCD Astrograph Catalog
\citep{2013AJ....145...44Z}, and the \textit{g'r'i'} magnitudes are
calibrated to SDSS Data Release 6 \citep{2008ApJS..175..297A}.

The Reionization and Transients InfraRed (RATIR) camera on the autonomous
1.5\,m Harold L. Johnson Telescope
\citep{2012SPIE.8446E..10B,2012SPIE.8444E..5LW} was used to observe \abc\ in
the $r'i'ZYJH$ filters. By design, RATIR lacks a cold shutter, which means
that IR dark frames are not available. Laboratory testing, however, confirms
that the dark current is negligible in both IR detectors
\citep{2012SPIE.8453E..1OF}.

The RATIR data were reduced, co-added, and analyzed using standard CCD and
IR processing techniques in \texttt{IDL}, \texttt{Python},
\texttt{SExtractor} \citep{1996A&AS..117..393B}, and \texttt{SWarp}.
Aperture photometry is obtained following the methods described in
\citet{2014AJ....148....2L}. The $r'i'Z$ filters are calibrated to SDSS
\citep{2014ApJS..211...17A}, while the $JH$ filters are calibrated to the
Two Micron All Sky Survey \citep{2006AJ....131.1163S}. For the $Y$-band
calibration, we used an empirical relation in terms of the $J$ and $H$
magnitudes derived from the United Kingdom Infrared Telescope (UKIRT;
\citealt{2007A&A...467..777C}) Wide Field Camera observations
\citep{2009MNRAS.394..675H}.

The \textit{Swift} satellite observed \abc\ on 14 epochs, beginning
$\sim$15\,days pre-maximum light through $\sim$22\,days post-maximum. The SN
flux is measured via aperture photometry on Ultraviolet-Optical Telescope
(UVOT) images via the usual procedures in \texttt{HEASoft}, including
corrections for coincidence loss and aperture loss. The image counts are
converted to physical fluxes using the latest calibration
\citep{2011AIPC.1358..373B}. There are no pre-SN UVOT images at the SN
location in the \textit{Swift} archive. Visual inspection of the UVOT images
suggests negligible host galaxy contamination in our UVOT flux measurements.
No X-ray emission is detected from \abc\ by the \textit{Swift} X-ray
Telescope (XRT).

The $g$-band discovery and follow-up data of \abc\ are illustrated in
Figure~\ref{fig:lightcurve}. The photometry is shown in the AB system. As
previously noted, the color terms necessary to convert $g_\mathrm{PTF}$ to
the AB system are unknown and assumed to be zero.

Spectroscopic observations of \abc\ were taken with a variety of telescopes
and instruments over multiple epochs beginning $\sim$2\,days after discovery
and ending $\sim$2\,months after $B$-band maximum. An observing log is
listed in Table \ref{tab:spec_obs_log}. The spectra were reduced using
standard procedures in \texttt{IDL}/\texttt{Python}/\texttt{Matlab}. The
optical spectral evolution of \abc\ is illustrated in Figure
\ref{fig:spec_seq}, which excludes high-resolution Very Large Telescope
(VLT) spectra for clarity.

\begin{deluxetable}{cccccc}
  \tablecaption{Spectroscopic observations of \abc\ \label{tab:spec_obs_log}}
  \tabletypesize{\footnotesize}
  \tablehead{
    \colhead{Observation} & \colhead{SN} & \colhead{} &
    \colhead{} & \colhead{Range} \\
    \colhead{MJD} & \colhead{Phase} & \colhead{Telescope} &
    \colhead{Instrument} & \colhead{(\AA)}
  }
  \startdata
  $57,483.26$ & $-15.9$ & DCT & DeVeny\tablenotemark{1} & $3301$--$7499$ \\
  $57,483.88$ & $-15.3$ & Gemini-north & GMOS\tablenotemark{2} & $3800$--$9200$ \\
  $57,484.51$ & $-14.7$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
  $57,486.51$ & $-12.7$ & Keck-II & DEIMOS\tablenotemark{3} & $5500$--$8099$ \\
  $57,488.38$ & $-10.9$ & Keck-I & LRIS\tablenotemark{4} & $3055$--$10411$ \\
  $57,489.51$ & $ -9.8$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$8999$ \\
  $57,490.40$ & $ -8.9$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
  $57,491.55$ & $ -7.8$ & LCO-2m & FLOYDS\tablenotemark{5} & $3300$--$9998$ \\
  $57,492.20$ & $ -7.2$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24550$ \\
  $57,494.00$ & $ -5.4$ & VLT & UVES\tablenotemark{7} & \\
  $57,503.32$ & $ +3.7$ & LCO-2m & FLOYDS\tablenotemark{5} & $3300$--$9999$ \\
  $57,506.00$ & $ +6.3$ & NOT & ALFOSC\tablenotemark{8} & $3602$--$8098$ \\
  $57,508.27$ & $ +8.5$ & LCO-2m & FLOYDS\tablenotemark{5} & $3301$--$9999$ \\
  $57,518.42$ & $+18.5$ & Keck-I & LRIS\tablenotemark{4} & $3071$--$10208$ \\
  $57,520.03$ & $+20.0$ & VLT & X-shooter\tablenotemark{6} & $3300$--$24789$ \\
  $57,529.40$ & $+29.2$ & LCO-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
  $57,542.41$ & $+41.9$ & LCO-2m & FLOYDS\tablenotemark{5} & $4000$--$8998$ \\
  $57,550.40$ & $+49.7$ & LCO-2m & FLOYDS\tablenotemark{5} & $4001$--$8999$ \\
  $57,562.38$ & $+61.4$ & LCO-2m & FLOYDS\tablenotemark{5} & $4800$--$9300$ \\
  \enddata
  \tablenotetext{1}{The Deveny Spectrograph \citep{2014SPIE.9147E..2NB}}
  \tablenotetext{2}{The Gemini Multi-Object Spectrograph \citep{2004PASP..116..425H}}
  \tablenotetext{3}{DEep Imaging Multi-Object Spectrograph \citep{2003SPIE.4841.1657F}}
  \tablenotetext{4}{Low-Resolution Imaging Spectrometer \citep{1995PASP..107..375O}}
  \tablenotetext{5}{FLOYDS;  \url{https://lco.global/observatory/instruments/floyds}}
  \tablenotetext{6}{X-shooter \citep{XShooter}}
  \tablenotetext{7}{Ultraviolet and Visual Echelle Spectrograph \citep{2000SPIE.4008..534D}}
  \tablenotetext{8}{The Andalucia Faint Object Spectrograph and Camera; \url{http://www.not.iac.es/instruments/alfosc}}
\end{deluxetable}

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=5.5in]{spectra.pdf}
  \caption{
  Observed spectral sequence of \abc. The spectra are normalized by their
  median flux between 6000 and 7000$\,\textrm{\AA}$. The phase of each
  spectrum relative to the time of $B$-band maximum is shown.
  Telluric absorption bands are grayed out. Line identifications are provided
  for the spectral features discussed in the text. For clarity,
  high-resolution spectra obtained with the VLT have been omitted (see
  \citealt{2017A&A...606A.111F}, for a detailed discussion of these spectra).}
  \label{fig:spec_seq}
\end{figure*}

@@

Separately, \citet{2015MNRAS.447.1531C} observe the 21\,cm line in NGC\,5221
and measure a redshift of $0.0234$, which we adopt for the remaining
analysis in this paper.

@@

A detailed study of the reddening toward \abc\ is presented in a companion
paper \citep{2017A&A...606A.111F}. Briefly, the foreground Galactic
extinction toward \abc\ is $E(B-V) = 0.0279$\,mag
\citep{2011ApJ...737..103S}. High-resolution spectra of \abc\ show multiple
absorption components for both the \ion{Ca}{2}\,H$+$K and \ion{Na}{1}\,D
doublets. Despite large equivalent widths (EWs) for these lines, implying
significant extinction (e.g., \citealt{2012MNRAS.426.1465P},
\citeauthor{2017A&A...606A.111F}~find evidence for only a small amount of
extinction. The empirical relation between the EW of \ion{Na}{1}\,D and
extinction has a large scatter, and \citet{2013ApJ...779...38P} have shown
that \ion{Na}{1}\,D absorption is a poor tracer of reddening in SNe Ia.
Thus, we adopt $E(B-V) = 0.05 \, \mathrm{mag}$ as the local extinction for
\abc\ \citep{2017A&A...606A.111F}. For the remainder of our analysis we
assume a total, Galactic$+$host galaxy, line-of-sight extinction of $E(B-V)
= 0.08 \, \mathrm{mag}$.

@@

Using the SuperNova IDentification (\texttt{SNID};
\citealt{2007ApJ...666.1024B}) package, we find that the low-resolution
spectrum of \abc\ at $+18.8$\,days is best matched by normal SNe Ia. Several
characteristic features of an SN Ia, such as \ion{Si}{2} and \ion{S}{2}, can
be easily identified in \abc\ (Figure \ref{fig:spec_seq}). From the $+3.7 \,
\mathrm{day}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs)
of $-12 \pm 2$\,\AA\ and $-55 \pm 5$\,\AA\ for the absorption features near
5750 and 6100 \AA, attributed to \ion{Si}{2}\,$\lambda\lambda$5972, 6355,
respectively. According to the \citet{2006PASP..118..560B} classification
scheme, \abc\ is a shallow-silicon SN, similar to 1999aa-like SNe
\citep{2009PASP..121..238B}. In Figure~\ref{fig:branch_vel, the velocity
evolution of the \abc\ \ion{Si}{2}$\,\lambda6355$ absorption minimum is
compared to the median evolution of the four spectroscopic subclasses from
\citet{2006PASP..118..560B}. The median evolution is defined using the
sample of SNe Ia in \citet{2012AJ....143..126B}. For each SN, we interpolate
the \ion{Si}{2} velocity, $v_{\mathrm{Si\,II}\,\lambda6355}$, to a fixed
grid at 1\,day intervals. The curves are defined by the median
$v_{\mathrm{Si\,II}\,\lambda6355}$ at each point on the grid with at least
three SNe (this prevents just one or two SNe from defining the evolution of
an entire subclass). The velocity evolution of \abc\ is most reminiscent of
the shallow-silicon subclass.}

@@

We measure the (pseudo-)bolometric luminosity, $L_\mathrm{UVOIR}$, of \abc\
at peak via trapezoidal integration of the reddening-corrected flux from the
UV, optical, and near-IR (UVOIR) filters. The light curves in the individual
filters are interpolated so that $L_\mathrm{UVOIR}$ is evaluated at common
epochs in each filter. From this integration, we measure a maximum
luminosity $L_\mathrm{max} = 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \;
s}^{-1}$ for \abc. This value is consistent with the normal SNe Ia studied
in \citet{2016A&A...588A..84D}. Following Arnett's rule
\citep{1982ApJ...253..785A, 1985Natur.314..337A}, the mass of $^{56}$Ni
synthesized in the explosion can be derived from $L_\mathrm{max}$. Assuming
a rise time of $19 \pm 3$\,days (see \citealt{2006A&A...450..241S}), we find
$M_\mathrm{Ni} = 0.6 \pm 0.1 M_\odot$.\footnote{A 17.9\,day rise time
(\S\ref{sec:lc_fit}), yields a consistent estimate of $M_\mathrm{Ni}$.}}

@@

Here we consider our suite of early observations of \abc and compare our
findings with SN\,2011fe, a well-studied, nearby SN that was discovered
shortly after explosion
\citep{2011Natur.480..344N,2012ApJ...744L..17B,2014ApJ...784...85P}.
